Local Group Satellite Alignments

### 2017-07-11 paper/paper.tex
table

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG satellite alignments]{Satellite Alignments in the Local Group}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

@@

\begin{itemize}
\item {\bf Stellar mass}. LGA galaxy pairs are composed by galaxies with stellar mass in the
range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
\item {\bf Dominant pair}. For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's separation.
\item {\bf Separation}. The distance between the galaxies' center of
  mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
\item {\bf Isolation}. For each galaxy in the pair there cannot be a galaxy more
  massive than the lightest galaxy in the pair within a radius of $2$
  Mpc. 
\end{itemize}

We find $19$ pairs of galaxies fulfilling these conditions.
Figure \ref{fig:samples} shows the radial velocity versus distance for
the LGA pairs.

@@

We place the LGA pairs into the cosmic web as quantified by the
deformation tensor  
\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
This method computes a cartesian grid the tensor 
\begin{equation}
T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j},
\end{equation}
%
where $\phi$ is a pseudo-gravitational potential that satisfies the
Poisson equation $\nabla^2\phi=\delta$, with $\delta$ the DM matter
overdentisy, and the $r_i$ coordinates correspond to a cartesian
system with $i=1,2,3$.

@@

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$M_{\star}$ & $10^{10}$\Msun & Stellar mass\\
$N_s$ & & Number of satellites with $M_V<-9$\\
$a > b> c$ & & Inertia tensor eigenvalues. \\
$\hat{s}_1$, $\hat{s}_2$, $\hat{s}_3$ & & Inertia tensor eigenvectors. \\
$\beta$  &  & Satellite Velocity Anisotropy\\
$\sigma_s$ & kpc & Plane width\\
$\lambda_1>\lambda_2>\lambda_3$ &  & Hessian Matrix
eigenvalues\\
$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ & - & Hessian Matrix
eigenvectors\\ 
$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}

@@

Following \cite{} we want to find the cosmic web preferential
direction towards which the vectors $\hat{r}_{AB}$, $\hat{s}_3$ and

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG satellite alignments]{Local Group Satellite Alignments}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\section{Observational Characterists of Andromeda and the Milky Way}
\label{sec:obs}

@@

\begin{itemize}
\item LGA galaxy pairs are composed by galaxies with stellar mass in the
range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
\item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's separation.
\item The distance between the galaxies' center of
  mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
\item For each galaxy in the pair there cannot be a galaxy more
  massive than the lightest galaxy in the pair within a radius of $2$
  Mpc. 
\end{itemize}

We find $19$ pairs with these conditions.
Figure \ref{fig:samples} shows the radial velocity versus distance for
the LGA pairs.

@@

We place the LGA pairs into the cosmic web as quantified by the
deformation tensor  
\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
This method computes a cartesian grid the tidal tensor 
\begin{equation}
T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j},
\end{equation}
%
where $\phi$ is a pseudo-gravitational potential that satisfies the
Poisson equation $\nabla^2\phi=\delta$, with $\delta$ the DM matter
overdentisy, and the $r_i$ coordinates correspond to a cartesian
system with $i=1,2,3$.

@@

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$M_{\star}$ & $10^{10}$\Msun & Stellar mass of the central galaxy\\
$N_s$ & & Number of satellites with $M_V<-9$\\
$a > b> c$ & & Inertia tensor eigenvalues. \\
$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
$\beta$  &  & Satellite Velocity Anisotropy\\
$\sigma_s$ & kpc & Plane width\\
$\lambda_1>\lambda_2>\lambda_3$ &  & Tidal tensor
eigenvalues\\
$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ &  & Tidal tensor
eigenvectors\\ 
$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}

@@

Following \cite{2014MNRAS.443.1090F} we compute the closest cosmic web
eigenvalue  towards which the vectors $\hat{r}_{AB}$, $\hat{p}$ and
$\hat{I}_a$ are aligned.
